Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-09-19 review_article.Rmd
move interactivity 3.2 to 3.4
steff

```{r ggcartograms, fig.cap = "Alternative maps of the United States of America. Each state has been coloured according to the average age-adjusted rate of incidence for lung and bronchus for females and males in the United States 2012-2016. Each stated shape has been distorted according to the population of the state in 2015. The state of California has become much larger due to it's large population density. This draws attention to the densely populated North East region, and detracts from the less populated Mid West.", message=FALSE, warning=FALSE, out.width='100%'}
usa1 <- png::readPNG("figures/ggcont.png")
usa2 <- png::readPNG("figures/ggncont.png")
usa3 <- png::readPNG("figures/ggdorl.png")
usa4 <- png::readPNG("figures/gghexmap.png")

library(cowplot)
ggdraw() +
  draw_plot(rasterGrob(usa1), 0, .5, 0.5, 0.5) +
  draw_plot(rasterGrob(usa2), 0.5, 0.5, 0.5, 0.5) +
  draw_plot(rasterGrob(usa3), 0.0, 0.0, 0.5, 0.5) +
  draw_plot(rasterGrob(usa4), 0.5, 0, 0.5, 0.5)+
  draw_plot_label(c("a", "b", "c", "d"), 
    c(0, .5, 0, 0.5), 
    c(1, 1, .5, .5), size = 15) +
  theme_set(theme_cowplot())
```

>>>>

```{r ggcartograms, fig.cap = "Alternative maps of the United States of America. Each state has been coloured according to the average age-adjusted rate of incidence for lung and bronchus for females and males in the United States 2012-2016. Each stated shape has been distorted according to the population of the state in 2015. The state of California has become much larger due to it's large population density. This draws attention to the densely populated North East region, and detracts from the less populated Mid West.", message=FALSE, warning=FALSE, out.width='100%'}
usa1 <- png::readPNG("figures/ggcont.png")
usa2 <- png::readPNG("figures/ggncont.png")
usa3 <- png::readPNG("figures/ggdorl.png")
#usa4 <- png::readPNG("figures/gghexmap.png")

library(cowplot)
ggdraw() +
  draw_plot(rasterGrob(usa1), 0, .5, 0.5, 0.5) +
  draw_plot(rasterGrob(usa2), 0.5, 0.5, 0.5, 0.5) +
  draw_plot(rasterGrob(usa3), 0.0, 0.0, 0.5, 0.5) +
  #draw_plot(rasterGrob(usa4), 0.5, 0, 0.5, 0.5)+
  draw_plot_label(c("a", "b", "c", "d"), 
    c(0, .5, 0, 0.5), 
    c(1, 1, .5, .5), size = 15) +
  theme_set(theme_cowplot())
```
